Topological Approach to Finding Blackholes in Large Directed Networks

### 2020-04-19 blackholes/pavt/article.tex
Small changes for russian supercomputer days

\begin{document}
\mainmatter              % start of a contribution
%
\title{Topological Approach to Finding Blackholes in Directed Networks}
%
\titlerunning{Topological Blackholes Mining}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Denis Ivanov\inst{1} \and Alexander Semenov\inst{2}}
%
\authorrunning{D. Ivanov, A. Semenov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Denis Ivanov and Alexander Semenov}
%
\institute{Lomonosov Moscow State University, Moscow, Russian Federation \\
\email{mr.salixnew@gmail.com}
\and
JSC NICEVT, Moscow, Russian Federation\\
\email{semenov@nicevt.ru}
}

@@

\begin{abstract}
In this paper we consider the problem of finding so called blackhole pattern in directed unweighted graphs.
Firstly, we analyse already existing algorithms and approaches. Secondly, we describe how structure of a graph
affects their efficiency. Then we introduce our approach to graph preprocessing. Finally, we describe topological sort based heuristic
and present results of experimental comparison between our approach and the previously developed algorithm.
\keywords{Directed networks $\cdot$ Subgraph mining $\cdot$ Blackhole pattern}
\end{abstract}

@@

The main contributor to the blackhole detecting problem is the authors from the University of New Jersey. They both formulated the task and proposed an algorithm for blackhole detection in case of unweighted directed graph \cite{li2010detecting}. 
Two years later they published an algorithm for approximate blackhole search in general case (weighted graph) \cite{li2012mining,li2014mining}. 
Hong et al \cite{hong2015detecting} consider application for online blackhole mining in the city environment. They introduced an original algorithm approximately solving the problem for dynamic graphs.

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Topological Approach to Finding Blackholes in Large Directed Networks}
%
\titlerunning{Topological Blackholes Mining}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Denis Ivanov\inst{1} \and Alexander Semenov\inst{2}}
%
\authorrunning{D. Ivanov, A. Semenov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Denis Ivanov and Alexander Semenov}
%
\institute{Lomonosov Moscow State University, Moscow, Russian Federation \\
\email{mr.salixnew@gmail.com}
\and
JSC NICEVT, Moscow, Russian Federation\\
\email{semenov@nicevt.ru}
}

@@

\begin{abstract}
In this paper we consider the problem of finding so called blackhole pattern in relatively large directed unweighted graphs.
Firstly, we analyse already existing algorithms and approaches. Secondly, we describe how structure of a graph
affects their efficiency. Then we introduce our approach to graph preprocessing. Finally, we describe topological sort based heuristic
and present results of experimental comparison between our approach and the previously developed algorithm.
\keywords{Directed networks $\cdot$ Subgraph mining $\cdot$ Blackhole pattern}
\end{abstract}

@@

The main contributor to the blackhole detecting problem is the authors from the University of New Jersey. They both formulated the task and proposed an algorithm for blackhole detection in case of unweighted directed graph \cite{li2010detecting}. 
Two years later they published an algorithm for approximate blackhole search in general case (weighted graph) \cite{li2012mining,li2014mining}. These works do not cover the case of large scale graphs, as the authors only run their algorithm on 1500 node networks, which is quite a small size.
Hong et al \cite{hong2015detecting} consider application for online blackhole mining in the city environment. They introduced an original algorithm approximately solving the problem for dynamic graphs.
